Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-06-03 article.rnw
Change values from being in breeding pairs to individuals.
Specify that initial densities are given in breeding pairs.
That sentence uses the word "pair" three times to refer to two different things:
breeding pairs, or pairs of species. Specifying that the first use is
breeding pairs should help lessen confusion.

The experiment used six species of \emph{Drosophila} from an Australian rainforest community: \emph{D. birchii}, \emph{D. pallidifrons}, \emph{D. pandora}, \emph{D. pseudoananassae}, \emph{D. simulans}, and \emph{D. sulfurigaster}.
The experiment took place in vials with a limited amount of medium for egg-laying and larval development; competition was for space on this medium.
A fixed number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
The number of adult pairs of each species emerging from these eggs was counted.

% DBS: Wait, the response is pairs? So can we have non-integer responses?

Experiments occurred for every single-species and two-species combination of the six species, at a variety of densities.
The single-species densities were 3, 9, or 12 pairs per vial, and each of these was replicated six times per species.
The two-species densities were (3,3), (3,6), (3,9), (3,12), (6,3), (9,3), or (12,3) pairs per vial (where the paired values give the densities of each of the two species), and each of these was replicated three times per pair of species.
Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.
Further details of the experimental methodology can be found in \textcite{terry2021natural}.

>>>>

The experiment used six species of \emph{Drosophila} from an Australian rainforest community: \emph{D. birchii}, \emph{D. pallidifrons}, \emph{D. pandora}, \emph{D. pseudoananassae}, \emph{D. simulans}, and \emph{D. sulfurigaster}.
The experiment took place in vials with a limited amount of medium for egg-laying and larval development; competition was for space on this medium.
A fixed number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
The number of adults of each species emerging from these eggs was counted.

Experiments occurred for every single-species and two-species combination of the six species, at a variety of densities.
The single-species densities were 3, 9, or 12 pairs per vial, and each of these was replicated six times per species.
The two-species densities were (3,3), (3,6), (3,9), (3,12), (6,3), (9,3), or (12,3) breeding pairs per vial (where the paired values give the densities of each of the two species), and each of these was replicated three times per pair of species.
Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.
Further details of the experimental methodology can be found in \textcite{terry2021natural}.
